Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_appendix_software_credit.tex
Minor fix to minor tweak

Major obstacles include the fact that indexers (e.g., Scopus, Web of Science,  Google Scholar) do not currently support software/data document types or  DataCite DOIs.
Therefore, even with universal association of scientific software with DOIs  and standized practices for citing software in publications, software citations will not be indexed in the same manner as traditional publications.

>>>>

Major obstacles include the fact that indexers (e.g., Scopus, Web of Science,  Google Scholar) do not currently support software/data document types or  DataCite DOIs.
Therefore, even with universal association of scientific software with DOIs and standardized practices for citing software in publications, software citations will not be indexed in the same manner as traditional publications.
